---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


<!-- badges: start -->
[![R-CMD-check](https://github.com/hughjonesd/rumpel/workflows/R-CMD-check/badge.svg)](https://github.com/hughjonesd/rumpel/actions)
<!-- badges: end -->

In the fairy tale, Rumpelstiltskin could be controlled once the heroine
learned his name. 

Rumpel is a tiny r package containing convenience functions for manipulating
objects by their names. Using these functions makes your code easier to read,
and reduces duplication:

```{r}
library(rumpel)
library(magrittr)
my_object <- c(One = 1, Two = 2, Three = 3, Four = 4)

# Base R:
my_object[startsWith(names(my_object), "T")]

# Nicer:
my_object %>% named_starting("T")


# Base R:
names(my_object)[names(my_object) %in% c("Two", "Three")] <-
      tolower(names(my_object)[names(my_object) %in% c("Two", "Three")])

# Nicer:
my_object %>% rename_in(c("Two", "Three"), tolower)
```



Functions that start with `named` return a subset of the original
object:

```{r}

vec <- c(One = 1, Two = 2, Three = 3, Four = 4)
vec %>% named_starting("T")
vec %>% named_like("[A-Z].*e$")
```

Functions that start with `rename` return the object with its
names changed:

```{r}
vec %>% rename_starting("T", tolower)
vec %>% rename_in(c("One", "Two"), paste, 1:2, sep = ".")
vec %>% rename_gsub("[aeiou]", "e")
```

Or you can use a one-sided formula, like in [purrr](https://purrr.tidyverse.org/):

```{r}
vec %>% rename_in(c("One", "Two"), ~paste(.x, 1:2, sep = "."))
```

Or you can just use a named character vector:

```{r}
vec %>% rename_in(c("One", "Two"), c(one = "One", two = "Two"))
```

Or an unnamed character vector:

```{r}
vec %>% rename_in(c("One", "Two"), c("First", "Second"))
```


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hughjonesd/rumpel")
```
