---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rumpel

<!-- badges: start -->
<!-- badges: end -->

Rumpel is a tiny r package containing convenience functions for manipulating
objects by their names. 

Functions that start with `named` return a subset of the original
object:

```{r}
library(rumpel)
library(magrittr)

vec <- c(one = 1, two = 2, three = 3, four = 4)
vec %>% named("one")
vec %>% named_like("^t")
```

Functions that start with `rename` return the object with its
names changed:

```{r}
vec <- c(one = 1, two = 2, three = 3, four = 4)
vec %>% rename_gsub("[aeiou]", "e")
vec %>% rename_toupper()
```

## Installation

You can install the released version of rumpel from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rumpel")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hughjonesd/rumpel")
```
