---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


<!-- badges: start -->
[![R-CMD-check](https://github.com/hughjonesd/namer/workflows/R-CMD-check/badge.svg)](https://github.com/hughjonesd/namer/actions)
<!-- badges: end -->


`{namer}` is a tiny r package containing convenience functions for manipulating
objects by their names. Using these functions makes your code easier to read,
and reduces duplication:

```{r}
library(namer)

vec <- c(One = 1, Two = 2, Three = 3, Four = 4)

# Base R:
vec[startsWith(names(vec), "T")]

# Clearer:
vec |> named_starting("T")


# Base R:
some_names <- names(vec) %in% c("Two", "Three")
names(vec)[some_names] <- tolower(names(vec)[some_names])

# Clearer:
vec |> rename_in(c("Two", "Three"), tolower)


# Base R:
vec[sort(names(vec))]

# Clearer:
vec |> sort_by_name()

```

Functions that start with `named` return a subset of the original
object:

```{r}

vec <- c(One = 1, Two = 2, Three = 3, Four = 4)
vec |> named_in(c("Two", "Three", "Non-existent"))
vec |> named_starting("T")
vec |> named_like("[A-Z].*e$")
```

`sort_by_name()` sorts object by name:

```{r}
sort_by_name(vec)
```

Functions that start with `rename` return the object with its
names changed. You can use a named character vector:

```{r}
vec |> rename_in(c("One", "Two"), c(one = "One", two = "Two"))
```

Or an unnamed character vector:

```{r}
vec |> rename_in(c("One", "Two"), c("First", "Second"))
```

Or a function:

```{r}
vec |> rename_all(tolower)
vec |> rename_starting("T", tolower)
```

Or you can use a one-sided formula, as in [purrr](https://purrr.tidyverse.org/):

```{r}
vec |> rename_in(c("One", "Two"), ~paste(.x, 1:2, sep = "."))
```

Or use a regular expression with `rename_gsub`:

```{r}
vec |> rename_gsub("[aeiou]", "e")
```

Or match names from old to new with `rename_lookup`:

```{r}
df <- data.frame(
        old = c("One", "Two", "Three", "Four"),
        new = c("A", "B", "C", "D")
      )
vec |> rename_lookup(df$old, df$new)
```

## Installation

You can install from R-universe:

``` r
install.packages("namer", repos = c("https://hughjonesd.r-universe.dev", 
                 "https://cloud.r-project.org"))
```

Or install the development version from [GitHub](https://github.com/):

``` r
# install.packages("remotes")
remotes::install_github("hughjonesd/namer")
```
